%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


  % \tllabelcventry{2020}{0}{2020///}{Team leader}{University of Luxembourg (LCSB)}{Luxembourg}{}
  % {Team Leader of the R3 IT infrastructure team, which works around change management and quality topics around reproducible science for the Luxembourg Systems Biomedicine institute (\textasciitilde 250 people) in the bioinformatics core group led by Dr Reinhard Schneider. This coordination includes managing a team of 12 colleagues. \newline{} For additional activities, see related \textit{Research Scientist} job entry below:
  % \begin{itemize}
  %   \item Responsible for the Resarch IT infrastructure of the LCSB (\textasciitilde 250 people). 
  %   \begin{itemize}
  %     \item Technical details: See \textit{Research Associate} job entry below.
  %   \end{itemize}
  %   \item Setup and responsible for the Laboratory (Lab) IT infrastructure of the LCSB;
  %   \item Bridge between Administrative IT (central) and institute IT activities;
  %   \item Manage and grow a team of 12 people;
  % \end{itemize}} 


%---------------------------------------------------------
  \cventry
    {University of Luxembourg - Luxembourg Centre for Systems Biomedicine (LCSB)} % 
    {Team Lead} % 
    {Esch-sur-Alzette, Luxembourg} % Location
    {2020-Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible to deliver Research IT services to the LCSB research institute (\textasciitilde 250 people).}
        \item {Define and implement change management and quality best practices on reproducble science for all research groups.}
        \item {Responsible for centralized (sensitive) data management and stewardship activities for the LCSB.}
        \item {Oversee policy development for sensitive reserch data and IT security.}
        \item {Lead public tender proposals.}
        \item {Oversee all technical platforms, such as virtualization clusters (\textgreater 300 virtual machines), storage backends (\textgreater 1 PiB) and core services such as institutional gitlab, wiki and lab support IT systems.}
        \item {Oversee the institute research software budget.}
        \item {Team size: 9-11}
      \end{cvitems}
    }

  \cventry
    {University of Luxembourg - Luxembourg Centre for Systems Biomedicine (LCSB)} % 
    {Research Scientist / Research Associate} % 
    {Esch-sur-Alzette, Luxembourg} % Location
    {2019-2020 / 2014-2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Setting up an institutional change management initative around reproducible science for the LCSB.}
        \item {Disseminate scientific results in journal publications and conferences.}
        \item {Setup core research IT platforms of the institute (OpenStack, Puppet, Foreman, freeIPA, Icinga, oVirt).}
        \item {Setup and maintain stroage systems for large research data (\textgreater 1 PiB).}
        \item {Established policies on data management for the institute.}
        \item {Develop tools to assist researchers data analysis workflows and data protection.}
      \end{cvitems}
    }

%----- 
  \cventry
    {IT for Translational Medicine - ITTM S.A.}
    {IT consultant}
    {Esch-sur-Alzette, Luxembourg}
    {2015-2018}
    {
      \begin{cvitems}
        \item {Provide various consulting services around IT and medical IT with a focus on strategy, security and IT architecture.}
      \end{cvitems}    
    }

%-----
  \cventry
    {Ernst \& Young Luxembourg} % 
    {Senior IT Auditor \& Consultant -- IT Risk \& Assurance team} % 
    {Munsbach, Luxembourg} % Location
    {2008-2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Carry out IT audits and IT consulting for various national and international clients.}
        \item {Activites include: IT effectiveness, cost optimization and service management; risk assessment and modeling; IT general controls, operations and infrastructure diagnostics.}
      \end{cvitems}
    }
\end{cventries}
